Minimizing post-shock forecasting error through aggregation of outside information

### 2020-12-19 Revision/manuscript.tex
revision comments for the first reviewer added
response to the second reviewer and editor but partial response to the associate editor

\begin{figure*}[t!]
  \begin{center}
    \subfloat{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}

@@

Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$. In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}. Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study. The details of this model are in the next section.

@@

We also consider the inverse-variance weighted estimator 
in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general.

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.

@@

Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.   In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$. 
From Proposition \ref{proprisk}, we obtain a risk-reduction condition
\begin{align}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
\end{align}

@@

If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
\begin{align} \label{varwadj}
\var{\hat{\alpha}_{\rm wadj}}
 &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
 &< \mu_{\alpha}^2.
\end{align}
In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice.  Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.

@@

\begin{prop}
\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
\end{prop}
Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} \\
 &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
 &< (\E{\alpha_1})^2,
\end{align*}
where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}. Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally. Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

@@

Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
  \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
\end{align*}
Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
  \begin{align}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{U}'_i\mbf{U}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
\end{align}
Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
 \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
 & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
\end{align*}
For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
\end{align*}
Under $\mc{M}_{22}$, we shall have
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}). In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.

@@

 \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
  \begin{align*}
   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
   = \mu_{\alpha}=\E{\alpha_1},
  \end{align*}
  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{U}_i$ is of full rank for all $i = 2, \ldots, n+1$. Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$. By Lemma \ref{risklemma}, 
    \begin{align*}
    R_{T_1^*+1,1}-R_{T_1^*+1,2}
    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
   &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
  \end{align*}
  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.

>>>>

\begin{figure*}[t!]
  \begin{center}
    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. \textcolor{red}{$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with. In this example,
    they differ only by an adjustment $\hat{\alpha}=10.22$.} It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}

@@

Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$. \textcolor{red}{In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.  We will assume that the donor pool time series are independent of the time series under study. The details of this model are in the next section.}

@@

We also consider the inverse-variance weighted estimator 
in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{M}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mbf{M}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general.

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, \textcolor{red}{where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}}.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.

@@

Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.   In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$. 
From Proposition \ref{proprisk}, we obtain a risk-reduction condition
\begin{align}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
\end{align}

@@

If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
\begin{align} \label{varwadj}
\var{\hat{\alpha}_{\rm wadj}}
 &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
 &< \mu_{\alpha}^2.
\end{align}
In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice.  Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.

@@

\begin{prop}
\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
\end{prop}
Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} \\
 &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
 &< (\E{\alpha_1})^2,
\end{align*}
where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}. Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally. Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. \textcolor{red}{Black dots and magenta line represent real data and fitted line, respectively.}}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

\textcolor{red}{We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$. Without loss of generality, we assume $m = 2$. There are two cases. First, suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.  Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.  The forecast at $t = T_1^* + 2$ is
\begin{align*}
  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
\end{align*} 
where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}. These two cases can be generalized to  forecasting $m\geq 2$ more periods. The scenarios for forecasting in AR($p$), or other general models are analogous.}

\textcolor{red}{In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.}

@@

Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
  \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
\end{align*}
Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
  \begin{align}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
\end{align}
Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
 \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
 & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
\end{align*}
For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
\end{align*}
Under $\mc{M}_{22}$, we shall have
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}). In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.

@@

 \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
  \begin{align*}
   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
   = \mu_{\alpha}=\E{\alpha_1},
  \end{align*}
  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{M}_i$ is of full rank for all $i = 2, \ldots, n+1$. Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$. By Lemma \ref{risklemma}, 
    \begin{align*}
    R_{T_1^*+1,1}-R_{T_1^*+1,2}
    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
   &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
  \end{align*}
  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.
